---
title: "TEST_p8105_hw6"
auther: "Liqi Zhou"
date: 2024-12-2
output: github_document
---

```{r message=FALSE, warning=FALSE}
library(tidyverse)
library(modelr)

set.seed(1202)
```

# Problem 1
```{r}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") |>
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10) |>
  select(name, id, everything())
```

### 1. A simple linear regression with tmax as the response and tmin as the predictor 
```{r}
lm_fit <- lm(tmax ~ tmin, data = weather_df)
```

### 2. Use 5000 bootstrap samples and produce estimates of $\hat{r}^2$ and $\log(\hat{\beta}_0 * \hat{\beta}_1)$
```{r}
bootstrap_function <- function(data) {
  boot_sample <- sample_frac(data, replace = TRUE)
  
  boot_fit <- lm(tmax ~ tmin, data = boot_sample)

  glance_result <- broom::glance(boot_fit)
  r_squared <- glance_result$r.squared
  
  beta <- coef(boot_fit)
  log_beta_product <- log(beta[1] * beta[2])
  
  return(tibble(
    r_squared = r_squared, 
    log_beta_product = log_beta_product))
}
```

```{r}
boot_straps_1 <- tibble(strap_number = 1:5000) |>
  mutate(
    strap_sample = map(strap_number, \(i) bootstrap_function(weather_df))
  ) |>
  unnest(strap_sample)

head(boot_straps_1, 5)
```

### 3. Plot the distribution of estimates
```{r}
ggplot(boot_straps_1, aes(x = r_squared)) +
  geom_density(color = "black", fill = "skyblue", alpha = 0.5) +
  labs(
    title = "Bootstrap Density Distribution of R-squared",
    x = "R-squared",
    y = "Density"
  )

ggplot(boot_straps_1, aes(x = log_beta_product)) +
  geom_density(color = "black", fill = "skyblue", alpha = 0.5) +
  labs(
    title = "Bootstrap Density Distribution of Log_beta_product",
    x = "Log_beta_product",
    y = "Density"
  )
```

**Description:**  
- $\hat{r}^2$: The distribution is bell-shaped, centered around 0.91, indicating that most R-squared estimates are concentrated near this value.  
- $\log(\hat{\beta}_0 * \hat{\beta}_1)$: The distribution is bell-shaped, centered around 2.02, indicating that most log estimates are concentrated near this value.  

### Identify the 2.5% and 97.5% quantiles to provide a 95% confidence interval for $\hat{r}^2$ and $\log(\hat{\beta}_0 * \hat{\beta}_1)$
```{r}
ci_r_squared <- quantile(boot_straps_1$r_squared, c(0.025, 0.975))
ci_log_beta_product <- quantile(boot_straps_1$log_beta_product, c(0.025, 0.975))

ci_r_squared
ci_log_beta_product
```
- CI of r_squared: (0.8939448, 0.9271188)  
- CI of log_beta_product: (1.964509, 2.058203)  


# Problem 2
```{r}
homicide_data <- read_csv("./data/homicide-data.csv")
```

### Create variables, omit variables, convert victim_age 
```{r warning=FALSE}
homicide_data_tidy <- homicide_data |>
  mutate(city_state = str_c(city, state, sep = ", "), 
         resolved = ifelse(disposition == "Closed by arrest", 1, 0)) |>
  filter(!city_state %in% c("Dallas, TX", "Phoenix, AZ", "Kansas City, MO", "Tulsa, AL"),
         victim_race %in% c("White", "Black")) |>
  mutate(victim_age = as.numeric(victim_age))

head(homicide_data_tidy, 5)
```

### Glm: resolved vs unresolved - victim age, sex and race in Baltimore, MD
a logistic regression:
```{r}
baltimore_data <- homicide_data_tidy |>
  filter(city_state == "Baltimore, MD")

baltimore_glm <- glm(resolved ~ victim_age + victim_sex + victim_race, 
                     data = baltimore_data, 
                     family = binomial)

baltimore_results <- broom::tidy(baltimore_glm)

baltimore_results
```

obtain the estimate and confidence interval of the adjusted odds ratio for solving homicides comparing male victims to female victims, keeping all other variables fixed:
```{r}
male_vs_female_results <- baltimore_results |>
  filter(term == "victim_sexMale") |>
  mutate(
    odds_ratio = exp(estimate),
    conf_low = exp(estimate - 1.96 * std.error),
    conf_high = exp(estimate + 1.96 * std.error)
  ) |>
  select(term, odds_ratio, conf_low, conf_high)

male_vs_female_results
```

### Apply the above steps to each of the cities
```{r}
city_or_results <- homicide_data_tidy |>
  group_by(city_state) |>
  nest() |>
  mutate(
    glm_fit = map(data, \(x) glm(resolved ~ victim_age + victim_sex + victim_race, data = x, family = binomial)),
    
    glm_tidied = map(glm_fit, \(x) broom::tidy(x)),
    
    or_results = map(glm_tidied, \(x) x |>
      filter(term == "victim_sexMale") |>
      mutate(
        odds_ratio = exp(estimate),
        conf_low = exp(estimate - 1.96 * std.error),
        conf_high = exp(estimate + 1.96 * std.error)
      )
    )
  ) |>
  unnest(cols = c(or_results)) |>
  select(city_state, odds_ratio, conf_low, conf_high)

head(city_or_results, 5)
```

### Create a plot that shows the estimated ORs and CIs for each city.
```{r}
ggplot(city_or_results, aes(x = reorder(city_state, odds_ratio), y = odds_ratio)) +
  geom_point() +
  geom_errorbar(aes(ymin = conf_low, ymax = conf_high), width = 0.2) +
  coord_flip() +
  labs(
    title = "Adjusted Odds Ratios for Solving Homicides by City",
    x = "City",
    y = "Odds Ratio (Male vs Female)"
  ) +
  theme_minimal()
```

**Comment:**  
- Most cities have odds ratios between 0.5 and 1, indicating that in these cities, male victims' cases are generally solved at a lower rate compared to female victims.  
- The width of the confidence intervals varies across cities, reflecting differences in data quantity and uncertainty. Some cities have very wide confidence intervals, indicating high uncertainty in the estimates.
